### 2015-02-20 fundamentals/impl.tex
more brevity

Simulation science - like experimental science - has since the beginning had the
problem of identifying trustworthy results from nonsensical results or noise.
Charles Babbage famously articulated this, ``On two occasions I have been asked,
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right
answers come out?' ... I am not able rightly to apprehend the kind of confusion
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
A simulator must both guard against the \emph{garbage in, garbage out} phenomenon, and also assure correctness.

>>>>

Simulation science - like experimental science - must identify trustworthy
results from nonsensical results or noise.
Charles Babbage famously articulated this, ``On two occasions I have been asked,
`Pray, Mr. Babbage, if you put into the machine wrong figures, will the right
answers come out?' ... I am not able rightly to apprehend the kind of confusion
of ideas that could provoke such a question.'' \cite{babbage_passages_2011}.
A simulator must assure correctness and guard against the \emph{garbage
in, garbage out} phenomenon.
